branching
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.path="inst/img/"
)
```

R client to fetch phylogenies from many places

To be included, with the associated function prefix:

* [Phylomatic](http://phylodiversity.net/phylomatic/) - `phylomatic`
* [Open Tree of Life](http://blog.opentreeoflife.org/) - `tol`

## Installation

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("sckott/branching")
```

```{r}
library("branching")
```

## Phylomatic

```{r}
taxa <- c("Poa annua", "Phlox diffusa", "Helianthus annuus")
tree <- phylomatic(taxa=taxa, get = 'POST')
plot(tree, no.margin=TRUE)
```

You can pass in up to about 5000 names. We can use `taxize` to get a random set of plant species names. 

```{r}
library("taxize")
spp <- names_list("species", 200)
out <- phylomatic(taxa = spp, get = "POST")
plot(out, show.tip.label = FALSE)
```

## Open Tree of Life

```{r}
taxa <- c("Poa annua", "Phlox diffusa", "Helianthus annuus")
tree <- phylomatic(taxa=taxa, get = 'POST')
plot(tree, no.margin=TRUE)
```

You can pass in up to about 5000 names. We can use `taxize` to get a random set of plant species names. 

```{r}
library("taxize")
spp <- names_list("species", 200)
out <- phylomatic(taxa = spp, get = "POST")
plot(out, show.tip.label = FALSE)
```
